\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\title{Research Assistant System}
\author{Team G.O.A.T\\
Besher Alkurdi, Bishwash Khanal, Abdelaziz Ibrahim}
\date{}

\begin{document}

\maketitle

\section*{Problem Domain: Education/Academics/Research}

\subsection*{Background}
\begin{itemize}
  \item Manual literature review is time consuming, one can miss relevant work
  \item A PhD student needs to quickly understand the state-of-the-art in a new field
  \item A research team wants to identify contradictory findings across multiple studies
\end{itemize}

\subsection*{Importance}
When writing papers, and when starting to research already explored ideas or to understand a topic deeply and find research gaps.

\subsection*{Challenges}
One of the primary challenges we face in research is dealing with information overload, as the sheer volume of available research papers can be overwhelming and difficult to manage effectively. It is challenging to thoroughly process and extract meaningful insights from each source. Additionally, assessing the relevance and reliability of these papers presents another hustle, as not all studies meet the same standards of quality or directly align with our research objectives. Beyond these issues, synthesizing findings across diverse studies adds a layer of complexity and forming a coherent understanding from a wide range of perspectives and methodologies.

\subsection*{Scenarios}

\subsection*{Scenario 1: Comprehensive Literature Collection}
\begin{itemize}[leftmargin=0.5in]
  \item \textbf{Challenge:} Researchers struggle to find all relevant papers across multiple databases and repositories.
  \item \textbf{Solution:} The Search Agent automatically queries multiple academic sources (Google Scholar, arXiv), collecting comprehensive results beyond what a human could manually gather.
\end{itemize}


\subsection*{Scenario 2: Content Analysis and Synthesis}
\begin{itemize}[leftmargin=0.5in]
  \item \textbf{Challenge:} Extracting key findings from dozens of papers is time-consuming and prone to oversight.
  \item \textbf{Solution:} The Analysis Agent reads papers, extracting methodologies and findings, while the Synthesis Agent connects related concepts across papers, identifying research gaps.
\end{itemize}

\end{document}